### 2017-10-26 paper.tex
nits

% \documentclass[10pt]{sosp2015}
% \documentclass[10pt,onecolumn]{sosp2015}
\documentclass[10pt,onecolumn,letterpaper]{article}
% \usepackage[10pt,inchmargins]{sigmin}  %% template from Xi Wang.
%\special{papersize=8.5in,11in}
%\setlength{\pdfpagewidth}{8.5in}
%\setlength{\pdfpageheight}{11in}
\usepackage[noheadfoot,
	      left=1in,right=1in,top=1in,bottom=1in,
             columnsep=0.3in
             ]{geometry}
\usepackage[small,compact]{titlesec}
\usepackage[font={small,bf}]{caption}    % added 9/10/13
\usepackage[nolineno,noindent,norules]{lgrind}
\usepackage{tightenum}
\usepackage{float}
\usepackage{xspace}
\usepackage{times,pifont}
\usepackage{mathptmx}
\usepackage{subfig,graphics,graphicx,color}
\usepackage{multirow}
\usepackage{dblfloatfix} %% correctly orders single- and double-col figures
\usepackage{hyphenat}
\usepackage{mathrsfs}
\usepackage{subfig}
\usepackage{amssymb,amsmath,centernot}
\usepackage{lastpage}
\usepackage{flushend}
\usepackage{hhline}
\usepackage{authblk}
%\newcommand{\doi}{XXXXXX}

%%% ================= START of SOSP '13 template ================= 
% \makeatletter
% 
% \def\ftype@copyrightbox{8}
% \def\@copyrightspace{
% \@float{copyrightbox}[b]
% \begin{center}
% \setlength{\unitlength}{1pc}
% \begin{picture}(20,6.0) 
% \put(0,3){\parbox{\columnwidth}{\scriptsize
% 
% %*** SAMPLE. AUTHOR PUT SUPPLIED TEXT HERE ****
% 
% \noindent
% \rule{6.0 cm}{0.2pt}\\
% Permissiondddd to make digital or hard copies of part or all of this work 
% for personal or classroom use is granted without fee provided that
% copies are not made or distributed for profit or commercial advantage 
% and that copies bear this notice and the full citation on the first
% page. Copyrights for third-party components of this work must be
% honored.  For all other uses, contact the Owner/Author. 
% 
% \vspace{\baselineskip}\noindent
% Copyright is held by the Owner/Author(s).\\
% \textit{SOSP'15}.\\
% ACM XXXXXXX.
% 
% \noindent
% http://dx.doi.org/\doi}
% }
% \end{picture}
% \end{center}
% \end@float}
% 
% \def\maketitle{\par
%  \begingroup
%    \def\thefootnote{\fnsymbol{footnote}}
%    \def\@makefnmark{\hbox
%        to 0pt{$^{\@thefnmark}$\hss}}
%      \twocolumn[\@maketitle]
% \@thanks
%  \endgroup
%  \setcounter{footnote}{0}
%  \let\maketitle\relax
%  \let\@maketitle\relax
%  \gdef\@thanks{}\gdef\@author{}\gdef\@title{}\gdef\@subtitle{}\let\thanks\relax
%  \@copyrightspace}
% 
% \makeatother

%%% ================= END of SOSP '13 template =================

%\newcommand{\comment}[1]{}
\frenchspacing

%\doublespacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     macro

\newcommand{\xxx}[0]{\textsc{Crane}\xspace}
\newcommand{\paxos}[0]{\textsc{Paxos}\xspace}
\newcommand{\mytitle}[0]{\textbf {Study Report}}
\newcommand{\mykeywords}[0]{State Machine Replication, Fault Tolerance, Stable 
and Deterministic Multithreading, Software Reliability}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% hyperref stuff

%\usepackage[square,comma,numbers,sort]{natbib}
\usepackage{hypernat}
\usepackage{hyperref}

%% fill in pdf info here
\hypersetup{%
colorlinks=false,
pdfborder={0 0 0},
pdftitle={\mytitle},
pdfkeywords={\mykeywords},
bookmarksnumbered,
pdfstartview={FitH},
urlcolor=cyan,
pdfpagelabels=true,
pdfdisplaydoctitle=true,
}%

%\usepackage{breakurl}
%\usepackage[all]{hypcap}
%\renewcommand{\url}{\burl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Some NICE fonts

\newfont{\BIG}{cminch}                             %--- One-inch font
\newfont{\sfbHuge}{cmssbx10 scaled\magstep5}       %-- 25pt sans serif bold
\newfont{\sfbLarger}{cmssbx10 scaled\magstep3}   %-- 12+pt sans serif boldd
\newfont{\sfblarger}{cmssbx10 scaled\magstep2}   %-- 12+pt sans serif bold
\newfont{\sfblarge}{cmssbx10 scaled\magstep1}      %-- 12pt sans serif bold
\newfont{\sfbeleven}{cmssbx10 scaled\magstephalf}  %-- 11pt sans serif bold
\newfont{\sfb}{cmssbx10}                           %-- 10pt sans serif bold
\newfont{\sfeight}{cmss8}                          %-- 8pt sans serif

%%%%%%%%%%%%%%%%%%%%%%%%
%    space tweaking

%\textwidth = 6.5 in
%\textheight = 9.0 in
%\setlength{\topmargin}{-.5in}

%\headheight = 0.0 in
%\headsep = 0.0 in
%\parskip = 0.2in
%\parindent = 0.0in

\renewcommand{\topfraction}{0.95}
\addtolength{\textfloatsep}{-0.1in}
%\addtolength{\floatsep}{0.025in}
\renewcommand\floatpagefraction{.9}
%\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}

\setlength{\parindent}{9pt}

% Rescue
\makeatletter
\def\v#1{{\mbox{\fontfamily{cmtt}\fontsize{\f@size}{\f@size}\selectfont #1}}}

\newcommand{\dmt}[0]{DMT\xspace}
\newcommand{\smt}[0]{StableMT\xspace}
\newcommand{\smr}[0]{SMR\xspace}

\newcommand{\racepro}[0]{\textsc{RacePro}\xspace}
\newcommand{\criu}[0]{\textsc{CRIU}\xspace}
\newcommand{\lxc}[0]{\textsc{LXC}\xspace}
\newcommand{\tern}[0]{\textsc{Tern}\xspace}
\newcommand{\peregrine}[0]{\textsc{Peregrine}\xspace}
\newcommand{\parrot}[0]{\textsc{Parrot}\xspace}
\newcommand{\repframe}[0]{\textsc{RepFrame}\xspace}
\newcommand{\grace}[0]{Grace\xspace}
\newcommand{\coredet}[0]{\textsc{CoreDet}\xspace}
\newcommand{\kendo}[0]{Kendo\xspace}
\newcommand{\dthreads}[0]{\textsc{DThreads}\xspace}
\newcommand{\determinator}[0]{Determinator\xspace}
\newcommand{\dos}[0]{dOS\xspace}
\newcommand{\ddos}[0]{DDOS\xspace}
\newcommand{\timealgo}[0]{time bubbling\xspace}
\newcommand{\ldpreload}[0]{LD\_PRELOAD\xspace}
\newcommand{\ntimeout}[0]{$W_{timeout}$\xspace}
\newcommand{\nclock}[0]{$N_{clock}$\xspace}

\newcommand{\apache}{\v{Apache}\xspace}
\newcommand{\mongoose}[0]{\v{Mongoose}\xspace}
\newcommand{\ab}{\v{ApacheBench}\xspace}
\newcommand{\clamav}{\v{ClamAV}\xspace}
\newcommand{\upnp}{uPnP\xspace}
\newcommand{\mediatomb}{\v{MediaTomb}\xspace}
\newcommand{\mencoder}{\v{mencoder}\xspace}
\newcommand{\mongodb}{\v{MongoDB}\xspace}
\newcommand{\ssdb}{\v{SSDB}\xspace}
\newcommand{\mysql}{\v{MySQL}\xspace}
\newcommand{\sysbench}{\v{SysBench}\xspace}
\newcommand{\zookeeper}{\v{ZooKeeper}\xspace}

\newcommand{\aget}[0]{\v{aget}\xspace}
\newcommand{\pthread}[0]{\mbox{Pthreads}\xspace}
\newcommand{\openldap}[0]{{OpenLDAP}\xspace}
\newcommand{\redis}[0]{{Redis}\xspace}
\newcommand{\bdb}[0]{{Berkeley DB}\xspace}
\newcommand{\vtune}[0]{\v{VTune}\xspace}
\newcommand{\http}[0]{\mbox{HTTP}\xspace}

% In short.
\newcommand{\eg}{{e.g.}}
\newcommand{\ie}{{i.e.}}
\newcommand{\etc}{{etc}}
\newcommand{\para}[1]{\vspace{.00in}\noindent{\bf #1}}
\newcommand{\wrt}{{w.r.t. }}
\newcommand{\cf}{{cf. }}

% Synch and network operations.
\newcommand{\checktimebubble}[0]{\v{check\_add\_timebubble()}\xspace}
\newcommand{\mutexlock}[0]{\v{pthread\_mutex\_lock()}\xspace}
\newcommand{\connect}[0]{\v{connect()}\xspace}
\newcommand{\send}[0]{\v{send()}\xspace}
\newcommand{\sendto}[0]{\v{sendto()}\xspace}
\newcommand{\sendmsg}[0]{\v{sendmsg()}\xspace}
\newcommand{\mywrite}[0]{\v{write()}\xspace}
\newcommand{\pwrite}[0]{\v{pwrite()}\xspace}
\newcommand{\close}[0]{\v{close()}\xspace}
\newcommand{\recv}[0]{\v{recv()}\xspace}
\newcommand{\select}[0]{\v{select()}\xspace}
\newcommand{\poll}[0]{\v{poll()}\xspace}
\newcommand{\epollwait}[0]{\v{epoll\_wait()}\xspace}
\newcommand{\accept}[0]{\v{accept()}\xspace}

% Parrot primitives.
\newcommand{\getturn}[0]{\v{get\_turn()}\xspace}
\newcommand{\putturn}[0]{\v{put\_turn()}\xspace}
\newcommand{\wait}[0]{\v{wait()}\xspace}
\newcommand{\signal}[0]{\v{signal()}\xspace}

% Evaluation stats.
\newcommand{\github}[0]{\url{github.com/columbia/crane}}
% \newcommand{\ntype}[0]{four\xspace}
\newcommand{\nprog}[0]{five\xspace}
\newcommand{\overheadmax}[0]{22.99\%\xspace}
\newcommand{\overhead}[0]{34.19\%\xspace}
\newcommand{\dmtspeedup}[0]{10.5\%\xspace}
\newcommand{\proxyoverhead}[0]{2.33\%\xspace}
\newcommand{\timebubblelow}[0]{66.65\%\xspace}
\newcommand{\timebubblehigh}[0]{93.88\%\xspace}
\newcommand{\recovertime}[0]{1.97ms\xspace}
\newcommand{\downgradetime}[0]{0.36s\xspace}
\newcommand{\mencoderspeedup}{\v{49\%}\xspace}

\newcommand{\us}[0]{\(\mu\text{s}\)\xspace}

\def\LGfsize{\footnotesize}
%\pagestyle{empty}

% \conferenceinfo{SOSP'15}{October 4--7, 2015, Monterey, CA}
% \copyrightyear{2015} 
% \copyrightdata{978-1-4503-3834-9/15/10} 
% \doi{2815400.2815427}

\title{\mytitle}
% \authorinfo{Authors}

% \author[+*]{Heming Cui}
% \author[*]{Rui Gu}
% \author[*]{Cheng Liu}
% \author[x]{Tianyu Chen}
% \author[*]{Junfeng Yang}
% \setlength{\affilsep}{0.5em}
% \renewcommand\AB@affilsepx{\hspace{28.0 mm}\protect\Affilfont}
% \affil[+]{\textrm\fontsize{10}{10}\selectfont The University of Hong Kong}
% \affil[*]{\textrm Columbia University}
% \affil[x]{\textrm Tsinghua University\vspace{-7.0 mm}}

\begin{document}

% Hack for: Package caption Error: No float type 'copyrightbox' defined.
%\newcounter{copyrightbox}

\date{}

\author[+]{Authors}
\maketitle
%\thispagestyle{empty}

% \begin{sloppypar}
% \begin{abstract}
% \input{abstract}
% \end{abstract}
% \end{sloppypar}

% \begin{sloppypar}
%% %\category{D.2.5}{Software Engineering}{Testing and Debugging}
%% \category{D.4.5}{Operating Systems}{Threads, Reliability}
%% \category{D.2.4}{Software Engineering}{Software/Program Verification}
%% \terms{Algorithms, Design, Reliability, Performance}
%% \keywords{\mykeywords}

%% \vskip 2mm
%% \noindent {\small \bf Categories and Subject Descriptors:} \vskip -.2mm
%% \noindent
%% {\footnotesize D.4.5~[{\bf Operating Systems}]: {Threads, Reliability}\\
%% D.2.4~[{\bf Software Engineering}]: {Software/Program Verification};}
%% \vskip 1mm
%% \noindent {\small \bf General Terms:} \vskip -.2mm
%% \noindent
%% {\footnotesize Algorithms, Design, Reliability, Performance}
%% \vskip 1mm
%% \noindent {\small \bf Keywords:} \vskip -.2mm
%% \noindent
%% {\footnotesize \mykeywords}

% \vskip 2mm
% \noindent {\small \bf Categories and Subject Descriptors:}
% {\small D.4.5~[{\bf Operating Systems}]: {Threads, Reliability};
%   D.2.4~[{\bf Software Engineering}]: {Software/Program Verification};}
% \vskip .1mm
% \noindent {\small \bf General Terms:} {\small Algorithms, Design,
%   Reliability, Performance}
% \vskip .1mm
% \noindent {\small \bf Keywords:} {\small \mykeywords}
% 
% \end{sloppypar}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Add page number.
\setcounter{page}{1}
\pagenumbering{arabic}

\thispagestyle{plain}
\pagestyle{plain}
\setlength{\footskip}{20pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{sloppypar}
% 
% \vskip 2mm
% \noindent {\small \bf Categories and Subject Descriptors:}
% {\small D.4.5~[{\bf Operating Systems}]: {Threads, Reliability};
%   C.2.4~[{\bf Computer-communication Networks}]: {Distributed Systems};}
% \vskip .1mm
% \noindent {\small \bf General Terms:} {\small Algorithms, Design,
%   Reliability, Performance}
% \vskip .1mm
% \noindent {\small \bf Keywords:} {\small \mykeywords}
% 
% \end{sloppypar}

\begin{sloppypar}
State machine replication (\smr) is a powerful fault-tolerance 
concept~\cite{paxos:practical}. It runs replicas 
of same program on multiple nodes. To keep the replicas consistent, it invokes a 
distributed consensus protocol (typically 
\paxos~\cite{paxos:simple,lamport98parttime,paxos:complex}) to ensure that a 
quorum (typically majority) of the replicas agree on the input request sequence. 
\smr is proven to tolerate various failure scenarios, like network 
partition and packet loss.

The fault-tolerant benefit of \smr makes it particularly an attractive 
high-availability service for general server programs. Unfortunately, despite 
much effort, existing \smr systems are still hard to deploy, mainly due to two 
problems.

The first problem is performance. The consensus latency of \paxos protocols is 
notoriously high and unscalable~\cite{zookeeper,glendenning2011scalable}, 
incurring high 
performance overhead for server programs. A main reason is that messages of 
traditional TCP or UDP-based \paxos protocols have to go through software 
network layers in OS kernels. For efficiency, \paxos 
protocols typically take the Multi-Paxos approach~\cite{paxos:simple}: it 
assigns one replica as the ``leader'' to invoke consensus requests, and the 
other replicas as ``backups'' to agree on requests. To agree on an input, at 
least one round-trip time (RTT) is required between the leader and a backup. 
Given that a ping RTT in LAN typically takes hundreds of \us, and that the 
request processing time of key-value store servers (\eg, \redis) is at most 
hundreds of \us, existing \paxos protocols incur high overhead in the response 
time of server programs.

Worse, the consensus latency of extant consensus protocols is often 
\emph{scale-limited}: it increases drastically when the number of concurrent 
requests or replicas increases. For instance, 
Scatter~\cite{glendenning2011scalable} shows that the consensus latency of its 
\paxos protocol increases by 1.6X when the number of replicas increases from 3 
to 9.

\begin{figure*}[ht]
\begin{center}
\includegraphics{figures/paxos_latency}
\caption{{\em Consensus latency of four existing consensus protocols.} All four 
protocols ran a client with 24 concurrent connections. The Y axis is broken to 
fit in all protocols.}\label{fig:paxos_latency}
\end{center}
\end{figure*}

To quantify this bottleneck, we evaluated four traditional consensus 
protocols~\cite{zookeeper, spaxos:srds12, crane:sosp15, libpaxos} on 24-core 
hosts with 40Gbps network, and we spawned 24 concurrent consensus connections. 
As shown in Figure~\ref{fig:paxos_latency}, when changing the replica group 
size from 3 to 9, although network and CPUs were not saturated, the consensus 
latency of 3 protocols drastically increased by 105.4\% to 168.3\%, and 36.5\% 
to 63.7\% of the increase was in OS kernel.

When only one consensus connection 
was spawned, the latency increase on the number of replicas was more gentle.

This evaluation shows that both the number of concurrent requests and 
replicas make consensus latency increase drastically. As modern server programs 
tend to support more concurrent client connections, and advanced SMR systems 
tend to deploy more replicas (\eg, Azure~\cite{azure:book} deploys seven or 
nine replicas) to support both replica failures and upgrades, the limited 
scalability in extant consensus protocols becomes even more pronounced.

The second problem is that most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage ZooKeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by ZooKeeper.

\end{sloppypar}

% uncomment to tweak with bib spacing
%\setlength\bibsep{2.25pt}
{
%\small
 \bibliographystyle{abbrv}
 \bibliography{bib/biblio}
}

\end{document}

### 2017-10-27 paper.tex
nits

@@
 
-The first problem is performance. The consensus latency of \paxos protocols is 
-notoriously high and unscalable~\cite{zookeeper,glendenning2011scalable}, 
-incurring high 
+First, the consensus latency of \paxos protocols is notoriously high and 
+unscalable~\cite{zookeeper,glendenning2011scalable}, incurring high 
 performance overhead for server programs. A main reason is that messages of 
@@
 latency of 3 protocols drastically increased by 105.4\% to 168.3\%, and 36.5\% 
-to 63.7\% of the increase was in OS kernel.
-
-When only one consensus connection 
+to 63.7\% of the increase was in OS kernel. When only one consensus connection 
 was spawned, the latency increase on the number of replicas was more gentle.
@@
 
-The second problem is that most existing \smr systems are not designed to 
-support unmodified server programs. To utilize existing \smr services, 
-developers often have to rewrite their code to orchestrate server programs into 
-the narrowly defined interfaces provided by these \smr systems. For instance, 
-to leverage ZooKeeper~\cite{zookeeper}, developers have to shoehorn their 
-programs into the file IO interface defined by ZooKeeper.
+Second, most existing \smr systems are not desgined to support unmodified 
+server programs. To utilize existing \smr services such as 
+ZooKeeper~\cite{zookeeper}, developers often have to rewrite their code to 
+shoehorn their programs into the narrowly defined state machine interfaces 
+provided by these \smr systems.
 

### 2017-10-27 paper.tex
nits

--- 2017-10-26 paper.tex
@@
 The second problem is that most existing \smr systems are not designed to 
-support unmodified server programs. To utilize existing \smr services, 
-developers often have to rewrite their code to orchestrate server programs into 
-the narrowly defined interfaces provided by these \smr systems. For instance, 
-to leverage ZooKeeper~\cite{zookeeper}, developers have to shoehorn their 
-programs into the file IO interface defined by ZooKeeper.
+support unmodified server programs. To utilize existing \smr services such as 
+ZooKeeper~\cite{zookeeper}, developers often have to rewrite their code 
+to orchestrate server programs into the narrowly defined interfaces 
+provided by these \smr systems.
 

### 2017-10-27 paper.tex
nits

--- 2017-10-26 paper.tex
@@
 \usepackage{authblk}
+\usepackage{booktabs}
 %\newcommand{\doi}{XXXXXX}
@@
 
-\newcommand{\xxx}[0]{\textsc{Crane}\xspace}
+\newcommand{\xxx}[0]{\textsc{APUS}\xspace}
 \newcommand{\paxos}[0]{\textsc{Paxos}\xspace}
@@
 \newcommand{\zookeeper}{\v{ZooKeeper}\xspace}
+\newcommand{\libpaxos}{libPaxos\xspace}
+\newcommand{\spaxos}[0]{S-Paxos\xspace}
+\newcommand{\crane}[0]{CRANE\xspace}
 
@@
 high-availability service for general server programs. Unfortunately, despite 
-much effort, existing \smr systems are still hard to deploy, mainly due to two 
-problems.
+much effort, existing \smr systems are still hard to deploy, mainly due to 
+three problems.
 
-The first problem is performance. The consensus latency of \paxos protocols is 
-notoriously high and unscalable~\cite{zookeeper,glendenning2011scalable}, 
-incurring high 
-performance overhead for server programs. A main reason is that messages of 
-traditional TCP or UDP-based \paxos protocols have to go through software 
-network layers in OS kernels. For efficiency, \paxos 
-protocols typically take the Multi-Paxos approach~\cite{paxos:simple}: it 
-assigns one replica as the ``leader'' to invoke consensus requests, and the 
-other replicas as ``backups'' to agree on requests. To agree on an input, at 
-least one round-trip time (RTT) is required between the leader and a backup. 
-Given that a ping RTT in LAN typically takes hundreds of \us, and that the 
-request processing time of key-value store servers (\eg, \redis) is at most 
-hundreds of \us, existing \paxos protocols incur high overhead in the response 
-time of server programs.
-
-Worse, the consensus latency of extant consensus protocols is often 
-\emph{scale-limited}: it increases drastically when the number of concurrent 
-requests or replicas increases. For instance, 
-Scatter~\cite{glendenning2011scalable} shows that the consensus latency of its 
-\paxos protocol increases by 1.6X when the number of replicas increases from 3 
-to 9.
+\textbf{High consensus latency.} The consensus latency of traditional \paxos 
+protocols is notoriously high, incurring high performance overhead for server 
+programs. A main reason is that messages of traditional TCP or UDP-based \paxos 
+protocols have to go through OS kernel. For efficiency, \paxos protocols 
+typically take the Multi-Paxos approach~\cite{paxos:simple}: it assigns one 
+replica as the ``leader'' to invoke consensus requests, and the other replicas 
+as ``backups'' to agree on requests. To agree on an input, at least one 
+round-trip time (RTT) is required between the leader and a backup. Given that a 
+ping RTT in LAN typically takes hundreds of \us, and that the request processing 
+time of key-value store servers (\eg, \redis) is at most hundreds of \us, 
+existing \paxos protocols incur high overhead in the response time of server 
+programs.
 
@@
 \caption{{\em Consensus latency of four existing consensus protocols.} All four 
-protocols ran a client with 24 concurrent connections. The Y axis is broken to 
-fit in all protocols.}\label{fig:paxos_latency}
+protocols ran a client with 24 concurrent connections.}\label{fig:paxos_latency}
 \end{center}
@@
 
-To quantify this bottleneck, we evaluated four traditional consensus 
+\textbf{Poor scalability.} The consensus latency of extant consensus protocols 
+is often \emph{scale-limited}: it increases drastically when the number of 
+concurrent requests or replicas 
+increases~\cite{zookeeper,glendenning2011scalable}.
+
+To quantify this problem, we evaluated four traditional consensus 
 protocols~\cite{zookeeper, spaxos:srds12, crane:sosp15, libpaxos} on 24-core 
-hosts with 40Gbps network, and we spawned 24 concurrent consensus connections. 
-As shown in Figure~\ref{fig:paxos_latency}, when changing the replica group 
-size from 3 to 9, although network and CPUs were not saturated, the consensus 
-latency of 3 protocols drastically increased by 105.4\% to 168.3\%, and 36.5\% 
-to 63.7\% of the increase was in OS kernel.
+hosts with 40Gbps network. For each protocol, we spawned 24 concurrent 
+consensus connections. As shown in Figure~\ref{fig:paxos_latency}, when 
+changing the replica group size from 3 to 9, the consensus latency of three 
+traditional protocols increased almost linearly to the number of replicas except 
+S-Paxos. S-Paxos batches requests from replicas and invokes consensus when the 
+batch is full. More replicas can take shorter time to form a batch, so S-Paxos 
+incurred a slightly better consensus latency with more replicas. Nevertheless, 
+its latency was always over 600\us.
 
-When only one consensus connection 
-was spawned, the latency increase on the number of replicas was more gentle.
+To find scalability bottlenecks in traditional protocols, we used only one 
+client connection and broke down their consensus latency on leader 
+(Table~\ref{tab:traditional-latency}). From 3 to 9 replicas, the consensus 
+latency (the ``Latency'' column) of these protocols increased more gently than 
+that on 24 concurrent connections. For instance, when the number of replicas 
+increased from three to nine, ZooKeeper latency increased by 30.3\% with one 
+connection; this latency increased by 168.3\% with 24 connections (Figure 1). 
+This indicates that concurrent consensus requests are the major scalability 
+bottleneck for these protocols.
+
+\begin{table}[h]
+\caption{{\em Performance breakdown of traditional protocols on leader
+with only one connection.} The ``Proto-\#Rep" column is the protocol name 
+and replica group size; ``Latency" is the consensus latency; ``First" 
+is the latency of leader's first received consensus reply; ``Major" is the
+latency of leader's consensus; ``Process" is leader's time spent in
+processing all replies; and ``Sys" is leader's time spent in systems (OS
+kernel, network stacks, and JVM) between the ``First" and ``Major" 
+reply. Times are in \us.}
+\label{tab:traditional-latency}
+\centering
+\begin{tabular}{lrrrrr}
+\toprule
+{\bf Proto-\#Rep} & {\bf Latency} & {\bf First} & {\bf Major} & {\bf
+Process}
+& {\bf Sys}\\
+\midrule
+\libpaxos-3 & 81.6 & 74.0  & 81.6 & 2.5 & 5.1\\
+\libpaxos-9 & 208.3 & 145.0  & 208.3 & 12.0 & 51.3\\
+
+\zookeeper-3 & 99.0 & 67.0  & 99.0 & 0.84 & 31.2\\
+\zookeeper-9 & 129.0 & 76.0  & 128.0 & 3.6 & 49.4\\
+
+\crane-3 & 78.0 & 69.0  & 69.0 & 13.0 & 0\\
+\crane-9 & 148.0 & 83.0  & 142.0 & 30.0 & 35.0\\
+
+\spaxos-3 & 865.1 & 846.0  & 846.0 & 20.0 & 0\\
+\spaxos-9 & 739.1 & 545.0  & 731.0 & 35.0 & 159.1\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Specifically, three protocols had scalable latency on the arrival of their 
+first consensus reply (the ``First'' column), which implies that network is not 
+saturated. \libpaxos is an exception because its two-round protocol consumed 
+much bandwidth. However, on the leader, there is a big gap between the arrival 
+of the first consensus reply and the ``majority'' reply (the ``Major'' column). 
+Given that the replies' CPU processing time was small (the ``Process'' column), 
+we can see that various systems layers, including OS kernel, network 
+libraries, and language runtimes (e.g., JVM), are another major scalable 
+bottleneck (the ``Sys'' column).
 
@@
 
-The second problem is that most existing \smr systems are not designed to 
+\textbf{Hard to use.} Most existing \smr systems are not designed to 
 support unmodified server programs. To utilize existing \smr services, 

### 2017-10-27 paper.tex
nits

@@
 \newcommand{\sysbench}{\v{SysBench}\xspace}
-\newcommand{\zookeeper}{\v{ZooKeeper}\xspace}
+\newcommand{\zookeeper}{ZooKeeper\xspace}
 \newcommand{\libpaxos}{libPaxos\xspace}
-\newcommand{\spaxos}[0]{S-Paxos\xspace}
-\newcommand{\crane}[0]{CRANE\xspace}
+\newcommand{\spaxos}{S-Paxos\xspace}
+\newcommand{\crane}{\textsc{Crane}\xspace}
 
@@
 
+\textbf{Poor scalability.} The consensus latency of extant consensus protocols 
+is often \emph{scale-limited}: it increases drastically when the number of 
+concurrent requests or replicas 
+increases~\cite{zookeeper,glendenning2011scalable}.
+
 \begin{figure*}[ht]
@@
 \end{figure*}
-
-\textbf{Poor scalability.} The consensus latency of extant consensus protocols 
-is often \emph{scale-limited}: it increases drastically when the number of 
-concurrent requests or replicas 
-increases~\cite{zookeeper,glendenning2011scalable}.
 
@@
 that on 24 concurrent connections. For instance, when the number of replicas 
-increased from three to nine, ZooKeeper latency increased by 30.3\% with one 
+increased from three to nine, \zookeeper latency increased by 30.3\% with one 
 connection; this latency increased by 168.3\% with 24 connections (Figure 1). 
@@
 the narrowly defined interfaces provided by these \smr systems. For instance, 
-to leverage ZooKeeper~\cite{zookeeper}, developers have to shoehorn their 
-programs into the file IO interface defined by ZooKeeper.
+to leverage \zookeeper~\cite{zookeeper}, developers have to shoehorn their 
+programs into the file IO interface defined by \zookeeper.
 

### 2017-11-02 paper.tex
nits

@@
 \newcommand{\crane}{\textsc{Crane}\xspace}
+\newcommand{\dare}{DARE\xspace}
 
@@
 
-\author[+]{Authors}
+\author[+]{}
 \maketitle
@@
 
+Although there are some hardware-accelerated consensus 
+protocols~\cite{consensusbox:nsdi16,netpaxos:sosr15,specpaxos:nsdi15,
+nopaxos:osdi16} which are effective on reducing consensus latency, they are 
+either unsuitable for general server programs or are not designed to be 
+scalable on concurrent client connections. For instance, 
+\dare~\cite{dare:hpdc15}, a novel consensus protocol, achieves the lowest 
+consensus latency on a small number of client connections, but both its 
+evaluation shows that its consensus latency increases quickly when  
+more connections are added. Other recent 
+works~\cite{nopaxos:osdi16,specpaxos:nsdi15,netpaxos:sosr15} 
+leverage in-network serialization in a datacenter to safely skip 
+consensus if packets arrive at replicas in the same order. 
+These works require reconstructing a server program to use their new libraries 
+for checking the order of packets, so they are not designed to run legacy 
+server programs.
+
 \end{sloppypar}

### 2017-11-03 paper.tex
nits

@@
 \newcommand{\paxos}[0]{\textsc{Paxos}\xspace}
-\newcommand{\mytitle}[0]{\textbf {Study Report}}
+\newcommand{\mytitle}[0]{\textbf {Problems on providing efficient fault 
+tolerance to programs}}
 \newcommand{\mykeywords}[0]{State Machine Replication, Fault Tolerance, Stable 
@@
 \begin{sloppypar}
+
 State machine replication (\smr) is a powerful fault-tolerance 
@@
 much effort, existing \smr systems are still hard to deploy, mainly due to 
-three problems.
+three problems as elaborated below.
 
-\textbf{High consensus latency.} The consensus latency of traditional \paxos 
-protocols is notoriously high, incurring high performance overhead for server 
-programs. A main reason is that messages of traditional TCP or UDP-based \paxos 
-protocols have to go through OS kernel. For efficiency, \paxos protocols 
-typically take the Multi-Paxos approach~\cite{paxos:simple}: it assigns one 
-replica as the ``leader'' to invoke consensus requests, and the other replicas 
-as ``backups'' to agree on requests. To agree on an input, at least one 
-round-trip time (RTT) is required between the leader and a backup. Given that a 
-ping RTT in LAN typically takes hundreds of \us, and that the request processing 
-time of key-value store servers (\eg, \redis) is at most hundreds of \us, 
-existing \paxos protocols incur high overhead in the response time of server 
-programs.
-
-\textbf{Poor scalability.} The consensus latency of extant consensus protocols 
+\subsection*{Issue 1: Poor scalability}
+The consensus latency of extant consensus protocols 
 is often \emph{scale-limited}: it increases drastically when the number of 
@@
 
-\textbf{Hard to use.} Most existing \smr systems are not designed to 
+\subsection*{Issue 2: Hard to use}
+Most existing \smr systems are not designed to 
 support unmodified server programs. To utilize existing \smr services, 
@@
 to leverage \zookeeper~\cite{zookeeper}, developers have to shoehorn their 
-programs into the file IO interface defined by \zookeeper.
+programs into the file IO interface defined by \zookeeper. As an another 
+example, in order to provide fault tolerance to a whole virtual machine, most 
+of the existing \smr systems need to modify the hypervisor code which can be 
+complex and error-prone.
+
+\subsection*{Issue 3: High Consensus Latency}
+
+The consensus latency of traditional \paxos 
+protocols is notoriously high, incurring high performance overhead for server 
+programs. A main reason is that messages of traditional TCP or UDP-based \paxos 
+protocols have to go through OS kernel. For efficiency, \paxos protocols 
+typically take the Multi-Paxos approach~\cite{paxos:simple}: it assigns one 
+replica as the ``leader'' to invoke consensus requests, and the other replicas 
+as ``backups'' to agree on requests. To agree on an input, at least one 
+round-trip time (RTT) is required between the leader and a backup. Given that a 
+ping RTT in LAN typically takes hundreds of \us, and that the request 
+processing 
+time of key-value store servers (\eg, \redis) is at most hundreds of \us, 
+existing \paxos protocols incur high overhead in the response time of server 
+programs.
 
@@
 \dare~\cite{dare:hpdc15}, a novel consensus protocol, achieves the lowest 
-consensus latency on a small number of client connections, but both its 
+consensus latency on a small number of client connections, but its 
 evaluation shows that its consensus latency increases quickly when  

### 2017-11-09 paper.tex
nits

@@
 \newcommand{\mytitle}[0]{\textbf {Problems on providing efficient fault 
-tolerance to programs}}
+tolerance to server programs}}
 \newcommand{\mykeywords}[0]{State Machine Replication, Fault Tolerance, Stable 
@@
 
-\subsection*{Issue 1: Poor scalability}
-The consensus latency of extant consensus protocols 
-is often \emph{scale-limited}: it increases drastically when the number of 
-concurrent requests or replicas 
-increases~\cite{zookeeper,glendenning2011scalable}.
+\subsection*{Issue 1: High Consensus Latency}
+
+The consensus latency of traditional \paxos 
+protocols is notoriously high, incurring high performance overhead for server 
+programs. A main reason is that messages of traditional TCP or UDP-based \paxos 
+protocols have to go through OS kernel. For efficiency, \paxos protocols 
+typically take the Multi-Paxos approach~\cite{paxos:simple}: it assigns one 
+replica as the ``leader'' to invoke consensus requests, and the other replicas 
+as ``backups'' to agree on requests. To agree on an input, at least one 
+round-trip time (RTT) is required between the leader and a backup. Given that a 
+ping RTT in LAN typically takes hundreds of \us, and that the request 
+processing 
+time of key-value store servers (\eg, \redis) is at most hundreds of \us, 
+existing \paxos protocols incur high overhead in the response time of server 
+programs.
+
+\subsection*{Issue 2: Poor scalability}
 
@@
 \end{figure*}
+
+The consensus latency of extant consensus protocols 
+is often \emph{scale-limited}: it increases drastically when the number of 
+concurrent requests or replicas 
+increases~\cite{zookeeper,glendenning2011scalable}.
 
@@
 
-\subsection*{Issue 2: Hard to use}
+\subsection*{Issue 3: Hard to use}
 Most existing \smr systems are not designed to 
@@
 complex and error-prone.
-
-\subsection*{Issue 3: High Consensus Latency}
-
-The consensus latency of traditional \paxos 
-protocols is notoriously high, incurring high performance overhead for server 
-programs. A main reason is that messages of traditional TCP or UDP-based \paxos 
-protocols have to go through OS kernel. For efficiency, \paxos protocols 
-typically take the Multi-Paxos approach~\cite{paxos:simple}: it assigns one 
-replica as the ``leader'' to invoke consensus requests, and the other replicas 
-as ``backups'' to agree on requests. To agree on an input, at least one 
-round-trip time (RTT) is required between the leader and a backup. Given that a 
-ping RTT in LAN typically takes hundreds of \us, and that the request 
-processing 
-time of key-value store servers (\eg, \redis) is at most hundreds of \us, 
-existing \paxos protocols incur high overhead in the response time of server 
-programs.
 

### 2017-11-12 paper.tex
nits

@@
 \newcommand{\mytitle}[0]{\textbf {Problems on providing efficient fault 
-tolerance to server programs}}
+tolerance to \\ server programs}}
 \newcommand{\mykeywords}[0]{State Machine Replication, Fault Tolerance, Stable 
@@
 to leverage \zookeeper~\cite{zookeeper}, developers have to shoehorn their 
-programs into the file IO interface defined by \zookeeper. As an another 
-example, in order to provide fault tolerance to a whole virtual machine, most 
-of the existing \smr systems need to modify the hypervisor code which can be 
-complex and error-prone.
+programs into the file IO interface defined by \zookeeper.
 
